Group 1: Tennis 

### 2019-12-11 Group1Prez.Rmd
Fixed picture
New Tourney Data

## Game of Tennis 
![](tennis-scoring.jpg){ width=85% }\

@@

Winner1 <- which(T1 == max(T1))
#Winner1

#T2<- table(base::sample(rownames(Tourney1_Women), 2000, prob = Tourney1_Women$Our.P.Winning.the.Tournement., replace = TRUE)) 
#Winner2 <- which(T2 == max(T2))
#Winner2

@@

Winner1 <- which(T1 == max(T1))
#Winner1

#T2<- table(base::sample(rownames(Tourney1_Men), 2000, prob = Tourney1_Men$Our.P.Winning.the.Tournement., replace = TRUE)) 
#Winner2 <- which(T2 == max(T2))
#Winner2

>>>>

## Game of Tennis

```{r,echo=FALSE, fig.align='center'}
include_graphics("Scoring.jpg")
```

@@

Winner1 <- which(T1 == max(T1))

ggplot(data.frame(T1)) +
  geom_col(aes(x=Var1, y=Freq/2000)) +
  xlab("Players") + 
  ylab("P(Winning the Tournement") +
  ggtitle("Which Player Won the Tournement?")

@@

Winner1 <- which(T1 == max(T1))

ggplot(data.frame(T1)) +
  geom_col(aes(x=Var1, y=Freq/2000)) +
  xlab("Players") +
  ylab("P(Win the Tournement)") +
  ggtitle("Which Player Won the Tournement?")

## 2019 Wimbledon: Women

```{r, warning=FALSE, echo=FALSE}
WimWomen <- read_csv("2019 Womens Wimbledon.csv")

WimWomen$`P(Winning a Rally)` <- WimWomen$`Points Won on Serve`/WimWomen$`Total Points Served`

WimWomen <- as.data.frame(WimWomen)

WimWomen$`P(Winning Tournement)`<- pTC(WimWomen[1,4][1], WimWomen[2,4][1],WimWomen[3,4][1],WimWomen[3,4][1],2)

T1<- table(base::sample(WimWomen$Name, 2000, prob = WimWomen$`P(Winning a Rally)`, replace = TRUE))

Winner1 <- which(T1 == max(T1))

ggplot(data.frame(T1)) +
  geom_col(aes(x=Var1, y=Freq/2000)) +
  xlab("Players") +
  ylab("P(Win the Tournement)")
  ggtitle("Which Player Won the Tournement?")

## 2019 Wimbledon: Men

```{r, warning=FALSE, echo=FALSE}
WimMen <- read_csv("2019 Men's Wimbledon.csv")

WimMen <- as.data.frame(WimMen)

WimMen$`P(Winning a Rally)` <- WimMen$`Points Won on Serve`/ WimMen$`Total Points on Serve`

WimMen$`P(Winning Tournement)`<- pTC(WimMen[1,4][1], WimMen[2,4][1],WimMen[3,4][1],WimMen[3,4][1],2)

T1<- table(base::sample(WimMen$Name, 2000, prob = WimMen$`P(Winning a Rally)`, replace = TRUE))

Winner1 <- which(T1 == max(T1))
